\ttitle

### 2014-01-06 Chapters/Chapter6.tex
WIP chapter 6

%----------------------------------------------------------------------------------------
\section{Outline}
\emph{Not intented for the reader.}
\begin{itemize}
  \item Apply proposed method to real-world applications, such as
    \begin{itemize}
      \item Daily life activity recognition (as the original context of this thesis is)
      \item PowerHouse sensor data
      \item Stock data?
    \end{itemize}
  \item Relate back to filter vs. wrapper methods - give results with different methods?
\end{itemize}

\input{./Chapters/Chapter6/data_gathering}

>>>>

In this chapter we discuss the real-world data sets used for this research and the performance of our proposed algorithm on these data sets.
In \Cref{sec:data_sets} we discuss common available data sets and argue that these are inappropriate for our research.
It is followed by an overview of the setup we have created to record our own continuous data sets in an uncontrolled environment, both for in- and outdoor activities.
The series of activities performed are discussed in \Cref{sec:data_gathering}.
In that section we show typical plots of the inertial sensor data and stills from the video recordings.
That will illustrate the setting in which the activities are performed and the characteristics of continuous data.
Finally, the results of the algorithm are discussed in \Cref{sec:real_world_results}.
We will use the objective measures, introduced in \Cref{sec:artificial_data_quality_metrics}, and also try to give subjective claims on the performance of the algorithm applied to the real-world data.

\input{./Chapters/Chapter6/data_sets}
\input{./Chapters/Chapter6/data_gathering}
\input{./Chapters/Chapter6/results}

### 2014-01-06 Chapters/Chapter6/data_gathering.tex
WIP chapter 6

\subsection{Outdoor straight lines}\label{subsec:outdoor_straight}
The first series of outdoor performed activities consist of walking and running segments in a straight line.
Halfway the recording is a $180^{\circ}$ turn.
The activities consist of standing still, walking and running (both jogging and sprinting).
The plots of \Cref{fig:plots_subject_1} shows the recordings of Subject $1$.
For Subject $2$ the plots are visible in \Cref{fig:plots_subject_2}.
The recorded metrics originate from the accelerometer, rotational and magnetometer sensors.
The solid black lines indicate manually annoted change points, the dashes lines indicate the closest discovered change point.
A still from the video recording, showing Subject $2$ performing a (sprinting) run segment, is in \Cref{fig:stills_subject_2_sprinting}.

@@

% ===== OUTDOOR FREE ACTIVITIES ========
\subsection{Outdoor free}\label{subsec:outdoor_free}
The second series of outdoor recordings consist of more free-form activities.
The performed activities consist, as with the first set, of standing, walking, and running.
Furthermore, the segments are performed in a circular manner.
\eg the running activities are performed around a fountain with an estimated diameter of 10 meters.
The plots of the recordings of Subject, for the accelerometer, rotation, and magnetometer are shown in...
\TODO{Add plots}
For Subject~$2$ the still of the video recordings are in the upper row of \Cref{fig:stills_subject_1_and_2}, for Subject~$1$ in the lower row.

@@

  \begin{subfigure}[b]{1\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_mag_annotated.eps}
    \caption{Magnetic Field}
    \label{fig:recording_subject_1_run_1_magnetic}
  \end{subfigure} \\
  \caption[Plots]{Annotated plots of a full recording performed by Subject~$2$. The vertical lines are manually determined change points. The label above each segment indicates the current performed activity.}\label{fig:plots_subject_1}
\end{figure}

>>>>

\subsection{Outdoor straight lines}\label{subsec:outdoor_straight}
The first series of outdoor performed activities consist of walking and running segments in a straight line.
Halfway the recording is a $180^{\circ}$ turn.
The activities consist of standing still, walking and running (both jogging and sprinting).
The plots of \Cref{fig:plots_subject_2} shows the recordings of Subject $2$.
The recorded metrics originate from the accelerometer, rotational and magnetometer sensors.
The solid black lines indicate manually annoted change points, the dashes lines indicate the closest discovered change point.
A still from the video recording, showing Subject $2$ performing a (sprinting) run segment, is in \Cref{fig:stills_subject_2_sprinting}.

@@

% ===== OUTDOOR FREE ACTIVITIES ========
\subsection{Outdoor free}\label{subsec:outdoor_free}
The second series of outdoor recordings consist of more free-form activities.
The performed activities consist, as with the first set, of standing, walking, and running.
Furthermore, the segments are performed in a circular manner.
\eg the running activities are performed around a fountain with an estimated diameter of 10 meters.
The plots of the recordings of Subject, for the accelerometer, rotation, and magnetometer are shown in...
\TODO{Add plots}
For Subject~$1$ the still of the video recordings are in the upper row of \Cref{fig:stills_subject_1_and_2}, for Subject~$2$ in the lower row.

@@

  \begin{subfigure}[b]{1\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_mag_annotated.eps}
    \caption{Magnetic Field}
    \label{fig:recording_subject_1_run_1_magnetic}
  \end{subfigure} \\
  \caption[Plots]{Annotated plots of a full recording performed by Subject~$2$. The vertical lines are manually determined change points. The label above each segment indicates the current performed activity.}\label{fig:plots_subject_2}
\end{figure}
